\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% Font package

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Shevinu Nawalage} \\ \vspace{5pt}
    40 Graves Street, St. John's, NL, CA \\ \vspace{3pt}
    \small \raisebox{-0.1\height}\faPhone\ 709-219-3095 ~ \href{mailto:shevinu.dev@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  {\textcolor{blue}{shevinu.dev@gmail.com}}} ~ 
    \href{http://shevinum.dev}{\raisebox{-0.2\height}\faGlobe\ {\textcolor{blue}{shevinum.dev}}}  ~
    \href{https://www.linkedin.com/in/shevinu-nawalage-a109371bb/}{\raisebox{-0.2\height}\faLinkedin\ {\textcolor{blue}{Shevinu Nawalage}}}  ~
    \href{https://github.com/ShevinuM}{\raisebox{-0.2\height}\faGithub\ {\textcolor{blue}{ShevinuM}}}
    \vspace{-2pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Memorial University of Newfoundland}{Sep. 2021 - April 2025}
      {Bachelor of Science in Computer Science (GPA: 3.91 / 4.0)}{St. John's, NL}
  \resumeSubHeadingListEnd
  
%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{1}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures and Algorithms
                \item Discrete Mathematics for Computer Science
                \item Software Engineering 
                \item OOP and Human-Computer Interaction
                \item Foundations of Computer Systems
                \item Computer Architecture and Design
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, HTML, CSS, SQL, JavaScript} \\
     \textbf{Developer Tools}{: PostgreSQL, Git, pip, VS Code, IntelliJ IDEA } \\
     \textbf{Technologies/Frameworks}{: JUnit, Swing, jQuery, Bootstrap} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\href{https://github.com/ShevinuM/Cant-Stop}{\textcolor{blue}{\textbf{Can't Stop}}} $|$ \emph{Java, Swing}}{January 2023 - April 2023}
          \resumeItemListStart
            \resumeItem{Collaborated with a team of four to develop a desktop game that digitally replicates the Can’t Stop Board Game.}
            \resumeItem{Specialized in back-end development, designed and implemented the game logic using Java, effectively translating the physical game rules into a virtual environment.}
            \resumeItem{Implemented a comprehensive algorithm to determine the relative positioning of the pieces on the board according to the dice rolls. Algorithm also determines the winner based of the dice positioning represented in multiple data structures}
            \resumeItem{Implemented load/save functionality through serialization utilizing Data Storage classes to save the current state of the board allowing for the future possibility of networking as well.}
          \resumeItemListEnd
          \vspace{-13pt}
        \resumeProjectHeading
          {\href{https://github.com/ShevinuM/Sheldon}{\textcolor{blue}{\textbf{Sheldon}}} $|$ \emph{Python, Flask, HTML, CSS, JavaScript, AWS Elastic Beanstalk}}{May 2023 - June 2023}
          \resumeItemListStart
            \resumeItem{Developed a responsive Full-Stack Chatbot application using OpenAI API, specifically tailored to respond to queries related to portfolio building, thereby streamlining user interaction.}
            \resumeItem{Implemented a persistent caching mechanism to optimize response times and significantly reduce the number of costly API calls.}
            \resumeItem{Leveraged AWS Elastic Beanstalk for efficient application deployment and management, ensuring high availability and scalable performance.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\href{https://github.com/ShevinuM/Personal-Portfolio}{\textcolor{blue}{\textbf{Personal Portfolio Page}}} $|$ \emph{JavaScript, HTML, CSS, jQuery, Bootstrap}}{June 2023}
          \resumeItemListStart
            \resumeItem{Developed a responsive and interactive personal portfolio website showcasing my personal projects and skills.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\href{https://github.com/ShevinuM/Data-Structures-And-Algorithms}{\textcolor{blue}{\textbf{Data Structures and Algorithms}}} $|$ \emph{Java, Python}}{}
          \resumeItemListStart
            \resumeItem{Comprehensive Repository consisting of my solutions and explanations to 90+ complex DSA problems.}
          \resumeItemListEnd
         \vspace{-13pt}
          \resumeProjectHeading
          {\href{https://github.com/ShevinuM/SafePass}{\textcolor{blue}{\textbf{SafePass}}} $|$ \emph{Java, JUnit}}{May 2023 - Present}
          \resumeItemListStart
            \resumeItem{Developed "SafePass," a secure desktop password manager, emphasizing local storage for improved data security.}
            \resumeItem{Enhanced security with PBKDF2 HmacSHA256 hashing and salting for reliable password storage.}
            \resumeItem{Built SafePass for extensibility, using plug-in interfaces, MVC design pattern, and core OOP concepts to create a scalable codebase.}
            \resumeItem{Ongoing: Utilizing Spring Boot for enhanced functionality and configuration, implementing a SQL database for data management, and creating a user-friendly interface with JavaFX.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Memorial University of Newfoundland - CITL}{Oct 2022 - April 2023}
      {Design and Development Assistant}{St. John's, NL}
      \resumeItemListStart
        \resumeItem{Designed and deployed interactive educational webpages and posters using HTML and CSS.}
        \resumeItem{Created instructive modules simplifying Windows, Mac, and Chrome OS operations for tech novices, bridging the knowledge gap and empowering users.}
        \resumeItem{ Performed an extensive usability analysis on the Brightspace website and proposed user-centric enhancements to bolster efficiency and user experience.}
      \resumeItemListEnd

%

\end{document}
